### 2021-04-23 input/proposal.tex
minors

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} highlights such consistency issue with
dynamic partitions, even in contexts where \processes have FIFO links,
\ie where \processes receive the messages in the order of their
sending. Both \Process~$a$ and \Process~$d$ add then delete their
partition concurrently. \Process~$c$ receives, delivers, and forwards
$\alpha_d^3$ followed by $\delta_d$. In the meantime, \Process~$b$
receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, both \Process~$c$ and \Process~$d$ deliver
the message about Partition $P_a$, for they did not have any known
partition at receipt time. On the contrary, \Process~$b$ delivers
$\alpha_d^1$, for it improves its distance to a known
source. \Process~$b$ then blocks \Process~$a$'s removal notification
$\delta_a$. It never reaches \Process~$c$ nor \Process~$d$. Also,
\Process~$c$ and \Process~$d$ do not deliver any $\alpha_d$ or
$\delta_d$ since they already delivered it. The system converges to an
inconsistent state where some \processes assume they belong to a
partition while it does not exist anymore. Naive propagation of
$\alpha$ and $\delta$ messages is insufficient to guarantee consistent
partitioning when each \process can add or delete its partition at any
time. \Processes need to exploit their local knowledge gathered over
message receipts.

>>>>

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} highlights such consistency issue with
dynamic partitions, even in contexts where \processes have FIFO links,
\ie where \processes receive the messages in the order of their
sending. Both \Process~$a$ and \Process~$d$ add then delete their
partition concurrently. \Process~$c$ receives, delivers, and forwards
$\alpha_d^3$ followed by $\delta_d$. In the meantime, \Process~$b$
receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC}, both \Process~$c$ and \Process~$d$ deliver
the message about Partition $P_a$, for they did not have any known
partition at receipt time. On the contrary, \Process~$b$ delivers
$\alpha_d^1$, for it improves its distance to a known
source. \Process~$b$ then blocks \Process~$a$'s removal notification
$\delta_a$. It never reaches \Process~$c$ nor \Process~$d$. Also,
\Process~$c$ does not deliver $\alpha_d$ and $\delta_d$ since it
already delivered it. The system converges to an inconsistent state
where some \processes assume they belong to a partition while it does
not exist anymore. Naive propagation of $\alpha$ and $\delta$ messages
is insufficient to guarantee consistent partitioning when any \process
can add or delete its partition at any time. \Processes need to
exploit their local knowledge gathered over message receipts.
